Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Arguments section): get_log3, print_log3, put_log3.

::: { #func.get_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

::: { #func.get_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.get_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.get_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

::: { #func.print_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.put_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

::: { #func.put_log3.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

@@

::: { #func.put_log3.args.arg2 .sidebar }
  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

@@

::: { #func.get_log3.args.arg3 .sidebar }
  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.

>>>>

::: { #func.get_log3.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log3.args.arg1) and  [arg2](#func.get_log3.args.arg2) arguments, respectively.

@@

::: { #func.get_log3.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.get_log3.args.arg2 .sidebar }
  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.get_log3.args.arg3 .sidebar }
  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log3.args.arg1) and  [arg2](#func.print_log3.args.arg2) arguments, respectively.

@@

::: { #func.print_log3.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.arg2 .sidebar }
  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.print_log3.args.arg3 .sidebar }
  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.

@@

::: { #func.put_log3.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log3.args.arg1) and  [arg2](#func.put_log3.args.arg2) arguments, respectively.

@@

::: { #func.put_log3.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.

@@

::: { #func.put_log3.args.arg2 .sidebar }
  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.

@@

::: { #func.put_log3.args.arg3 .sidebar }
  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
